The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-02-06 repeater-vladata.tex
flux dist

**Does this flat distribution explain FRB flux flatness?**

Assuming that \frb\ is representative of the overall FRB population, we can use the energy distribution of the former to explore the flux distribution of the latter. We use a Monte-Carlo technique to simulate an FRB population with a given energy/luminosity and spatial distribution. To reproduce the observed FRB sample, we select the brightest $N$\ bursts and fit their fluxes with a powerlaw. The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}. Therefore, we sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.

These simulations confirm previous work that shows that in many circumstances the cumulative flux distribution follows a Euclidean distribution \citep[index $=-1.5$;][]{2016MNRAS.462..941L}. To reproduce the flatness (index $\approx-1$) of the observed flux distribution, we need to incorporate other effects. 
**in progress** (new figure?)

@@

\subsection{FRB Flux Distribution}
The Lorimer burst was surprising for its unusually high brightness with a lack of lower-significance detections. With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. This fact was recently demonstrated by yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.

**Discussion of energy/flux distribution analysis presented in \S \ref{sec:disn})**

>>>>

@@

\subsection{FRB Flux Distribution}
The Lorimer burst was surprising for its unusually large flux with a lack of lower-significance detections. As more FRBs have been detected, it has become clear that the FRB population has a relatively flat flux distribution \citep[cumulative flux distribution index $-0.5<\alpha<-1$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. This fact was recently demonstrated by yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.

Assuming that the \frb\ energy distribution is typical of FRBs, we can use it to simulate FRB populations and compare their flux distributions to the observed distribution. First, we assume an FRB population that is uniformly distributed in space from redshifts $z1$\ to $z2$. For each FRB source, we sample one FRB burst luminosity from a powerlaw distribution and calculate its flux.
%(uniform for energies from $10^{38}$\ to $10^{40}$; \S \ref{sec:disn} 
We sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.
We can show that the flux distribution powerlaw is --1.5 for a standard candle-like luminosity distribution at low redshift. For distributions out to $z2>1$, the distribution flattens slightly ($sim0.3$ in the index) due to cosmological space distortions.
For a large ($N\sim2000) population of such bursts, we select the brightest $M\sim20$\ to represent the flux-limited FRB sample of known FRBs...
The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}. 
We then fit the flux distribution of those $M$\ events with a powerlaw.

These simulations confirm previous work that shows that...
The cumulative flux distribution follows a Euclidean distribution \citep[index $=-1.5$;][]{2016MNRAS.462..941L} when...
Flatness has been observed...
This requires...
